Structuring Theories with Implicit Morphisms

### 2019-02-11 implicit.tex

In that case, we treat $\icl{S}$ as an abbreviation for $\icl{i(S)}$, where $i(S)$ is the pushout of $S$ along $i$ (see \cite{rabe:howto} for details on \mmt pushouts).
If $L'\harr L$, this reduces to the original semantics.
\end{example}

>>>>

In that case, we treat $\icl{S}$ as an abbreviation for $\icl{i(S)}$, where $i(S)$ is the pushout of $S$ along $i$ (see \cite{rabe:howto:14} for details on \mmt pushouts).
If $L'\harr L$, this reduces to the original semantics.
\end{example}

### 2019-02-11 intro.tex

\paragraph{Previous Work}
Implicit morphism were first conceived by Rabe in 2010 and implemented as part of the Twelf system \cite{twelf} (which implements the dependent type theory LF).
The theory behind this implementation was never written up and not published.
But the implementation already scaled well, and implicit morphisms were used in the LATIN logic atlas \cite{CHKMR:latinabs} built by Rabe and others in 2009--2012.
The LATIN atlas already has around a 1000 theories and atomic morphisms, and about 50 of the latter are marked as implicit.
It also has a few hundred inclusions, each of which induces another implicit morphism.

>>>>

\paragraph{Previous Work}
Implicit morphism were first conceived by Rabe in 2010 and implemented as part of the Twelf system \cite{twelf} (which implements the dependent type theory LF).
The theory behind this implementation was never written up and not published.
But the implementation already scaled well, and implicit morphisms were used in the LATIN logic atlas \cite{CHKMR:latinabs:11} built by Rabe and others in 2009--2012.
The LATIN atlas already has around a 1000 theories and atomic morphisms, and about 50 of the latter are marked as implicit.
It also has a few hundred inclusions, each of which induces another implicit morphism.

### 2019-02-11 paper.tex

\bibliographystyle{alpha}
\bibliography{../../../../frabe/Program_Data/Latex/bib/rabe,../../../../frabe/Program_Data/Latex/bib/systems,../../../../frabe/Program_Data/Latex/bib/institutions,../../../../frabe/Program_Data/Latex/bib/pub_rabe,../../../../frabe/Program_Data/Latex/bib/historical}

>>>>

\bibliographystyle{alpha}
\bibliography{macros/pub_rabe,macros/rabe,macros/systems}
